\paragraph{} An agile design process will be used during the development of this system. Our clients have given us many of the features that we will need to include in the final product, but there are more features that can be added if we find that we have extra time towards the end of the project. We will incorporate many of the same features of the previous system which will be described in greater detail later in this document. However, because we are utilizing a different platform that uses a different input method (touch screen versus keyboard and mouse) we will make several changes to make the product more user friendly.

\paragraph{} By using a agile scrum based development process we will be able to track our progress more easily. We will also be able to break the project down in to distinct features. This will allow us to focus on small parts and not get lost in the whole of the project. We plan to test the product at various stages of integration to ensure that we have not regressed and work out any potential problems that we encounter before they become blocks to our progress.

\subsection{Sprints}
\paragraph{} A sprint is a defined period of time when a task should be completed. At the beginning of each sprint the team will discuss which tasks will be completed with our client and ourselves. During the sprint each team member will work to complete the tasks that were assigned to them for that sprint. If a team member completes all of the work they were assigned for a sprint they can work on items for the next sprint or work on items that are currently in the backlog or icebox. For this project our sprints will be one week long.