%Template

%\begin{description}
%    \item[Use Case] \hfill \\
%    \item[Description] \hfill \\
%    \item[Actors] \hfill \\
%    \item[Preconditions] \hfill \\
%        \begin{enumerate}
%        \end{enumerate}
%    \item[Main Flow] \hfill \\
%        \begin{enumerate}
%        \end{enumerate}
%    \item[Alternate Flow] \hfill \\
%    \item[Postconditions]
%        \begin{enumerate}
%        \end{enumerate}
%\end{description}

\newcommand{\myspace}{\vspace{.5cm}}

\subsubsection{Main Menu / Usage Selection}
\begin{description}
    \item[Description] \hfill \\
        The user will be prompted to select an action, whether to take a new photo or analyze an existing photo.
    \item[Actors] \hfill \\
        User
    \item[Preconditions] \hfill \\
            N/A
    \item[Main Flow] \hfill 
        \begin{enumerate}
            \item Main menu is displayed.
            \item User selects to take a new picture.
                [Alt Flow 1: User selects to analyze an existing picture]
            \item User is taken to picture capture screen.
        \end{enumerate}
    \item[Alternate Flow] \hfill 
        \begin{enumerate}
            \item User selects to analyze an existing picture
                \begin{enumerate}
                    \item User is taken to the upload page.
                \end{enumerate}
        \end{enumerate}
    \item[Postconditions]
        N/A
\end{description}
\myspace

\subsubsection{Capture Picture}
\begin{description}
    \item[Description] \hfill \\
        The user captures the picture of the target and iSanta will normalize it for bullet hole detection.
    \item[Actors] \hfill \\
        User
    \item[Preconditions] \hfill 
        \begin{enumerate}
            \item User has a target for analyzing.
        \end{enumerate}
    \item[Main Flow] \hfill 
        \begin{enumerate}
            \item User takes a picture of the target.
            \item System normalizes the target.
            \item System approximates bullet hole location(s).
            \item System displays bullet hole adjustment screen to user.
        \end{enumerate}
    \item[Alternate Flow] \hfill \\
        \begin{enumerate}
        	   \item User cancels operation
	   	\begin{enumerate}
			\item User is returned to the previous menu.
		\end{enumerate}
	\end{enumerate}
    \item[Postconditions]
        \begin{enumerate}
            \item Bullet hole locations are approximated on the target.
            \item User has opportunity to adjust iSanta's estimates.
        \end{enumerate} 
\end{description}
\myspace

\subsubsection{Adjust Bullet Holes}
\begin{description}
    \item[Description] \hfill \\
        The user will be able to see where iSanta has predicted bullet holes on the target and will move, add, or subtract bullet holes from the spread.
    \item[Actors] \hfill \\
        User
    \item[Preconditions] \hfill 
        \begin{enumerate}
            \item Target has been uploaded.
            \item Target has been normalized and bullet hole locations have been detected.
            \item Adjustment screen is currently visible.
        \end{enumerate}
    \item[Main Flow] \hfill 
        \begin{enumerate}
            \item Target with bullet hole approximations are presented to the user.
                [Alt Flow 1: User cancels operation]
            \item User adjusts bullet hole locations using touch screen 
                [Alt Flow 2: User adds a bullet hole; 
                Alt flow 3: User subtracts a bullet hole]
            \item User submits adjusted target to system for analyzing. 
        \end{enumerate}
    \item[Alternate Flow] \hfill 
        \begin{enumerate}
            \item User cancels operation 
                \begin{enumerate}
                    \item Return user to main menu. 
                \end{enumerate}
            \item User adds a bullet hole
                \begin{enumerate}
                    \item Get bullet hole location from user.
                    \item Add bullet hole to list of locations and display on target.
                    \item Return to main flow 1.
                \end{enumerate}
            \item User subtracts a bullet hole
                \begin{enumerate}
                    \item Obtain which hole to remove.
                    \item Remove hole from target.
                    \item Return to main flow 1.
                \end{enumerate}
        \end{enumerate}
    \item[Postconditions]
        \begin{enumerate}
            \item List of bullet hole locations are saved for analyzing.
            \item All bullet holes are accounted for and are accurately placed.
        \end{enumerate}
\end{description}
\myspace

\subsubsection{Display Statistics}
\begin{description}
    \item[Description] \hfill \\
        The system will analyze the spread and display the statistics to the user on screen.  The screen will contain an option to export the results (e-mail, csv file)
    \item[Actors] \hfill \\
        User, iOS E-mail
    \item[Preconditions] \hfill 
        \begin{enumerate}
            \item Statistics have been calculated using the statistics engine. (This is done when the user chooses to display statistics.)
        \end{enumerate}
    \item[Main Flow] \hfill 
        \begin{enumerate}
            \item Display statistics screen to user.
            \item User selects to export the statistics via e-mail.
                [Alt Flow 1: User exits program]
            \item System compiles a readable format to send the files in.
            \item User is taken to iOS e-mail with the report as the text.
        \end{enumerate}
    \item[Alternate Flow] \hfill 
        \begin{enumerate}
            \item User exits program.
            \item Save no information but the picture.
        \end{enumerate}
    \item[Postconditions] \hfill
        \begin{enumerate}
            \item No report is saved internally.
        \end{enumerate}
\end{description}
